A thesis draft

### 2018-11-26 res/sections/15-ArchitecturalImplementation.tex
Start second attempt - revision one

After the Kubernetes configuration and installation, we started working for a
viable intergation between Kubernetes and Openbaton. Our first idea is the one
illustrated in Figure~\ref{chap:archimpl:sec:secondattempt:img:schema1}:
Openbaton, that had the TOSCA definitions, had to somehow convert these
definition in a suitable YAML for Kubernetes, that had in turn to elaborate it
and schedule to one minion in the cluster. The monitoring and management would
remain untouched, as we planned to create an image with the integrated EMS tools
that provided a seamless integration with Docker container. With this setting,
the only thing remained was to solve the issue of converting TOSCA definitions in
YAML one.
The first thing we started thinking about was how to perform the conversion.
% TODO talk about the problems of mapping the TOSCA definition from Openbaton
% with the Kubernetes elements (which we actually solved), and talk about how we
% weren't able to develop a VNFM plugin for Openbaton, and describe how Harbor
% born from it.

>>>>

After the Kubernetes configuration and installation, we started working for a
viable intergation between Kubernetes and Openbaton. Our first idea is the one
illustrated in Figure~\ref{chap:archimpl:sec:secondattempt:img:schema1}:
Openbaton, that had the TOSCA definitions, had to somehow convert these
definition in a suitable YAML for Kubernetes, that had in turn to elaborate it
and schedule to one minion in the cluster. The monitoring and management would
remain untouched, as we planned to create an image with the integrated EMS tools
that provided a seamless integration with Docker container. With this setting,
the only thing remained was to solve the issue of converting TOSCA definitions
in YAML one. The first thing we started thinking about was how to perform the
conversion. This topic was quite important because the TOSCA definition does not
really consider the possibility to have an alternative virtualization system
apart from the hypervisor one. This causes the TOSCA definition to be, in our
opinion, too much focused on the resources usage and regarding granularity
aspects such the deployment flavour and the kind of virtual link (concept that
does not really exsits in container based systems) to instatiate. Nonetheless,
we performed a mapping between most of the TOSCA keywords with some of the YAML
definition, in a way that a TOSCA configuration file was able to generate a
valid YAML deployment. After that, we started thinking instead who, in the
current architecture, had the task to perform this operation. Initially we
though that Kubernetes itself could have been a perfect candidate. From a
received TOSCA, a Kubernetes component should have validated and translated the
TOSCA definition to generate a YAML suitable to be finally submitted to the
Kubernetes API Server. Another feasible approach could have been to create a
Openbaton plugin in order to take the TOSCA to deploy and convert it before
submitting it to Kubernetes. This solution had great advantages in terms of
responsability separation: in this way only the MANO had to know, for a VIM
based on Kubernetes, that a conversion needed to be performed. From a Kuberentes
point-of-view, nothing would have changed, since all the configuration
conversion would have been performed by Openbaton.

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.7]{OpenbatonMANO}
  \caption[Openbaton architecture components]{Openbaton architecture components,
    taken from~\cite{openbatondocumentation}.}
  \label{chap:archimpl:sec:secondattempt:img:openbatonMANO}
\end{figure}

We started inspecting the Openbaton framework, to identify possible modules
where the conversion should have taken place. We identified first the VIM
driver, that is the component that directly interacts with the VIM, and then the
VNFM, because we discovered there were programmatic dipendences between the two
Openbaton standard components. After we identified the VIM driver and the VNFM
as components to be rewritten and to be adapted to the Kubernetes VIM, we
studied the original components code. We discovered that regarding these
components the documentation was very poor, especially regarding the code. On
top of that, the program interfaces given by the develpers did not match our
expectations: we thought to find interfaces indipendent from the type of the
virtualization technology, instead, we found that they were strictly coupled
with frameworks like Openstack or cloud vendors like Google Compute engine or
Amazon AWS. These reasons, with the fact that after two weeks we were not able
to get any working prototype of VIM driver or VNFM we gave up, searching for
another solution.

\section{Second attempt - revision one}

The impossibility to develop a custom VIM driver and VNFM manager lead us to
search for an alternative solution. Then, we started work directly on the VIM.
The base approach was to create an API Server which in future an Openbaton
plugin could contact and simply deploy TOSCA definitions, interacting with a set
of RESTful API.

% TODO talk about the problems of mapping the TOSCA definition from Openbaton
% with the Kubernetes elements (which we actually solved), and talk about how we
% weren't able to develop a VNFM plugin for Openbaton, and describe how Harbor
% born from it.
